---
title: "Boston"
author: "Abdullah Almarqabi"
date: "11/9/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

The Boston housing data set Contains information collected in 1970 by the U.S. Census Service around Boston, Massachusetts, and first appearing in a 1978 publication [1].


## Quick look


```{r cars}
library(MASS)
data("Boston")
summary(Boston)
```

## Sources of bias

The variable called "black" is calculated using the formula  B = 1000(Bk – 0.63)2 where Bk is the proportion of Black people per town.

With this variable, even doing simple data exploration like measuring the correlations between variables might suggest a relation between house prices and the proportion of black people in an area.

While not meaning to racially profile neighborhoods, this outdated data set might lead to racist interpretations without understanding the historical contexts.



## References


[1] Harrison, D. and Rubinfeld, D.L. Hedonic prices and the demand for clean air, J. Environ. Economics & Management, vol.5, 81-102, 1978




