---
title: "Ethics Package"
author: "Abdullah Almarqabi"
date: "15/11/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r development, include=FALSE}
library(testthat)
library(markdown)
library(MASS)
```

# Introduction
The Ethics R package aims to bridge the gap between ethics and the R working environment. The package provides tips and comments on data sets and models that highlights any ethical issues, biases or any tips on how to improve the models further.

# The goal
The goal is to have this package open sourced for others to add comments and tips on different data sets, models and more. This will make this package a library of ethics accessible easily for any R user

# Purpose
During the DS boot camp, the Boston housing data set was talked about with its biases and ethical issues it has. However, if a new data scientist worked with the data set without being informed about its issues it might lead to wrong correlations and conclusions. To solve problems similar to this, it would be fast and convenient to have these information and tips on the R environment to check quickly whenever needed.

```{r description, eval=FALSE}
# Describe your package
fusen::fill_description(
  pkg = here::here(),
  fields = list(
    Title = "Ethics Package",
    Description = "Provide ethical comments and guidelines on data sets and models.",
    `Authors@R` = c(
      person("Abdullah", "Almarqabi", email = "a.almarqabi@gmail.com", role = c("aut", "cre"), comment = c(ORCID = "0000-0002-1565-9313")),
      person(given = "ThinkR", role = "cph")
    )
  )
)
# Define License with use_*_license()
usethis::use_mit_license("Abdullah Almarqabi")
```

# Creating the package
The package was created with the help of the "Fusen" package. Fusen helps in creating packages easily from a simple markdown file. 


# Functionality
Currently, the package has two functions. The "ethics" function, which provides short comments and tips. Secondly, the "ethics_long" function that displays a detailed markdown file on the ethics of the input. Since the package is still a work in progress, for data sets, the package is applicable on the Boston data set. Furthermore, it gives comments on Linear models and Logistic models.

<!-- Store your dataset in a directory named "inst/" at the root of your project -->
<!-- Use it for your tests in this Rmd thanks to `load_all()` to make it available
and `system.file()` to read it in your examples 
-->

```{r development-2}
# Run all in the console directly
# Create "inst/" directory
dir.create(here::here("inst"))
# Example dataset
# file.copy(system.file("nyc_squirrels_sample.csv", package = "fusen"), here::here("inst"))
# Make your dataset file available to the current Rmd
pkgload::load_all(path = here::here(), export_all = FALSE)
# You will be able to read your example data file in each of your function examples and tests as follows
# datafile <- system.file("nyc_squirrels_sample.csv", package = "Ethics")
# nyc_squirrels <- read.csv(datafile)
```


# Function 1: Short ethics comments and tips

```{r function}
#' ethics
#'
#' @param x Data set or model
#' @inheritParams 
#'
#' @return
#' Comments and guidelines
#' @export
#' @example
ethics <- function(x) 
{
  if(class(x) =='lm')
    {
    cat("This is of class lm.
    
Tips for linear models: 
- Check for collinearity. It can be difficult to separate out the individual effects of collinear variables on the response. collinearity can cause predictor variables to appear as statistically insignificant when in fact they are significant.

- If collinearity or multicollinearity are present, you can implement Principal Component Regression PCR.")
    }
       else if(class(x) =='glm')
    {
    cat("This is a logistic regression model.
    
Tips for logistic regrission models:
- In case of multinomial classification, the assumptions will increase and the stability of the coefficient estimates and accuracy will decrease. In that case, more advanced models like regulization would be more adequate")

    }
    else if(x== Boston || x=="Boston")
      {
    cat("This is the Boston Housing data set.
    
- Source of bias: The data set has a (Black) coloumn which indicates the proportion of Black people per town. This could lead to racially discriminatory correlations.

- Many books and sites have removed the data set. It is recommended to not use it.

For more details use (ethics_long) function")
    }
  else 
    {
    cat("No information available")
    }
  
}


```

# Example
```{r examples}
library(Ethics)
ethics(Boston)
```



# Function 2: Detailed ethics comments

```{r function-1}
#' Detailed ethics comments
#'
#' @param x Data set or model
#' @inheritParams 
#'
#' @return
#' Opens markdown file
#' @export
#' @example
ethics_long <- function(x) 
{
  if(x== Boston || x=="Boston" )
      {
      rmarkdown::run("Boston.Rmd")
      
    }
  else 
    {
    cat("No information available")
    }
  
}


```

```{r examples-1}
ethics_long(Boston)
```





```{r development-1, eval=FALSE}
# Run but keep eval=FALSE to avoid infinite loop
# Execute in the console directly
fusen::inflate(rmd = "dev/dev_history.Rmd")
```

# Conclusion
In conclusion, there is a need to bridge the gap between ethics and writing code. To bridge this gap, the Ethics package provides these tips on any ethical concerns or ways to decrease the biases and improve the accuracy of a model. However, there are still huge rooms for improvements and additions for this package to be generalizable and easy to use for everyone.

# Limitations & Future devolopements
* More data sets need to be included in the package.
* The package needs to be able to read the specific model and give personal tips on how to improve it.
* Comments on graphs and plots need to be added for example

<!-- # Inflate your package

You're one inflate from paper to box.
Build your package from this very Rmd using `fusen::inflate()`

- Verify your `"DESCRIPTION"` file has been updated
- Verify your function is in `"R/"` directory
- Verify your test is in `"tests/testthat/"` directory
- Verify this Rmd appears in `"vignettes/"` directory -->
